---
output: html_document
title: "Web Appendix for AEA CSQIEP Seminar"
subtitle: "Public insurance, HIV, and risky behaviours: The role of PrEP"
date: "`r format(Sys.time(), '%d %B %Y')`"
---




```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

  ## Run dependencies
    
    source('code/functions/presentationDependencies.R')
    
    source('code/4.x.makePresentationFigs.R')
    

```

&nbsp;

# Author Contact Info

```{r author-info, warning=F, echo=F, include=T, message=F}

  
  tribble(~'Author', ~'Email', ~'Website',
          "Shyam Raman", "sr2297@cornell.edu", "https://shyamraman.weebly.com/",
          "Ben Harrell", "benjamin.harrell@vanderbilt.edu", "https://www.benharrellecon.com/",
          "Alex Hollingsworth", "hollinal@indiana.edu", "https://hollina.github.io/",
          "Sam Mann", "samuel.j.mann@vanderbilt.edu", "https://sites.google.com/view/samueljamesmann/home",
          "Katherine Wen", "kjw229@cornell.edu", "https://www.katherinewen.com/") %>% 
  knitr::kable() %>% kable_styling(full_width = T)


```

&nbsp;

# Data Access for Study

```{r data-sources, warning=F, echo=F, include=T, message=F}

  
  tribble(~'Data Source', ~'Years', ~'Access Link',
          "CDC Surveillance", "2008 to 2019", "https://www.cdc.gov/nchhstp/atlas/index.htm",
          "SEER Population Estimates",  "2008 to 2019", "https://seer.cancer.gov/popdata",
          "BLS LAU Estimates", "2008 to 2019", "https://www.bls.gov/lau/",
          "Medicaid SDUD", "2011 to 2019","https://www.medicaid.gov/medicaid/prescription-drugs/state-drug-utilization-data/index.html",
          "USC-RAND OPTIC", "2008 to 2019", "https://www.rand.org/health-care/centers/optic/resources/datasets.html") %>% 
  knitr::kable() %>% kable_styling(full_width = T)


```

&nbsp;
&nbsp;
&nbsp;
&nbsp;


# Distribution of STI Incidence Rates {.tabset .tabset-fade}

&nbsp;

## HIV {.tabset .tabset-fade .tabset-pills}

### Total Population


```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$hiv_tot


```

### By Gender

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$hiv_sex


```

### By Expansion Status

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$hiv_medexp


```

## Chlamydia {.tabset .tabset-fade .tabset-pills}

### Total Population


```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$chlamydia_tot


```

### By Gender

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$chlamydia_sex


```

### By Expansion Status

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$chlamydia_medexp


```


## Gonorrhea {.tabset .tabset-fade .tabset-pills}

### Total Population


```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$gonorrhea_tot


```

### By Gender

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$gonorrhea_sex


```

### By Expansion Status

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$gonorrhea_medexp


```

## Syphilis {.tabset .tabset-fade .tabset-pills}

### Total Population


```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$syphilis_tot


```

### By Gender

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$syphilis_sex


```

### By Expansion Status

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$dist$syphilis_medexp


```











&nbsp;
&nbsp;
&nbsp;
&nbsp;




&nbsp;
&nbsp;
&nbsp;
&nbsp;

# Stacked DiD Coefficient Plots {.tabset .tabset-fade .tabset-pills}

&nbsp;
&nbsp;

## HIV 
```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$coefplots$hiv_main 


```

## Chlamydia

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$coefplots$chlamydia_main 


```

## Gonorrhea

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$coefplots$gonorrhea_main 


```

## Syphilis

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$coefplots$syphilis_main 


```


&nbsp;
&nbsp;
&nbsp;
&nbsp;

# Event Studies for STI Incidence {.tabset .tabset-fade}

&nbsp;

## HIV {.tabset .tabset-fade}

### Total Population {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_total 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_a55plus 


```



### Among Men {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_male 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_male_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_male_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_male_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_male_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_male_a55plus 


```

#### MSM Transmission

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_msm 


```


### Among Women {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_male 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_female_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_female_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_female_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_female_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$hivdx_female_a55plus 


```







## Chlamydia {.tabset .tabset-fade}

### Total Population {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_total 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_a55plus 


```


### Among Men {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_male 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_male_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_male_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_male_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_male_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_male_a55plus 


```



### Among Women {.tabset .tabset-fade .tabset-pills}

#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_male 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_female_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_female_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_female_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_female_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$chlamydia_female_a55plus 


```









## Gonorrhea {.tabset .tabset-fade}

### Total Population {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_total 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_a55plus 


```


### Among Men {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_male 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_male_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_male_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_male_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_male_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_male_a55plus 


```



### Among Women {.tabset .tabset-fade .tabset-pills}

#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_male 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_female_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_female_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_female_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_female_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$gonorrhea_female_a55plus 


```






































## Syphilis {.tabset .tabset-fade}

### Total Population {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_total 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_a55plus 


```


### Among Men {.tabset .tabset-fade .tabset-pills}


#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_male 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_male_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_male_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_male_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_male_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_male_a55plus 


```



### Among Women {.tabset .tabset-fade .tabset-pills}

#### All Ages

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_male 


```

#### Aged 13 to 24

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_female_13_24


```

#### Aged 25 to 34

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_female_25_34 


```

#### Aged 35 to 44

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_female_35_44


```

#### Aged 45 to 54

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_female_45_54


```

#### Aged 55+

```{r, warning=F, echo=F, include=T, message=F, fig.width=12, fig.height=6}

figs$es_plots_cdc$syphilis_female_a55plus 


```












&nbsp;
&nbsp;
